The function-sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-08-25 crelle-dictionary.tex
Added etale descent reference

\begin{proof}
Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$
from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
\end{proof}

>>>>

\begin{proof}
Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}. 
In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$
from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
\end{proof}
